Local Spectral Clustering of Density Upper Level Sets

### 2019-06-16 neurips/local_spectral_density_clustering_arxiv.tex
just a checkpoint for me

@@

Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}. In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs. The proof of Theorem \ref{thm: mixing_time_upper_bound} is then carried out in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}. \ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.

@@

Lemma \ref{lem: expansion_volume} allows us to reason about the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.

@@

	We next show a lower bound on $\nu(\Asig)$. Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
	\begin{equation*}
	\Aset_{\sigma}^{(i)} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
	\end{equation*}
	Observe that $\bigcup_{i = 1}^{N} \Asig^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{(i)}$. As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
	\begin{align*}
	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{(i)}) \\
	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
	\end{align*}
	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
	\begin{equation*}
	\Aset_{\sigma + \delta + \epsilon}^{(i)} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
	\end{equation*}

	As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
	\begin{equation*}
	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{(i)}
	\end{equation*}
	and therefore
	\begin{align*}
	\nu(\Aset + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{(i)}\bigr) \\
	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{(i)})}{\nu(B(x_i,\sigma))}
	\end{align*}
	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
\end{proof}

We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.

\begin{lemma}
	\label{lem: covering}
	For $i = 1, \ldots, N$ and  $A_{\sigma}^{(i)}, A_{\sigma + \delta + \epsilon}^{(i)}$ as in Lemma \ref{lem: expansion_volume},
	\begin{equation*}
	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{(i)})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{(i)})}{\nu(B(x_i, \sigma))}
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
	\begin{equation*}
	\biggl(\Aset_{\sigma + \delta'}^{(i)} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{(i)} - \set{x_i}\biggr) 
	\end{equation*}
	since then
	\begin{equation*}
	\nu(\Aset_{\sigma + \delta'}^{(i)}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{(i)}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{(i)}).
	\end{equation*}

	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{(i)}$, meaning
	\begin{equation}
	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
	\end{equation}
	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$. Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
	\begin{equation*}
	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
	\end{equation*}
	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{(i)}$.
\end{proof}

We will need to carefully control the volume of expansion sets using the estimate in Lemma \ref{lem: expansion_volume}; Lemma \ref{lem: Taylor_series} serves this purpose.
\begin{lemma}
	\label{lem: Taylor_series}
	For any $0 \leq x \leq 1/2d$,
	\begin{align*}
	(1 + x)^d & \leq 1 + 2\dx \\
	(1 - x)^d & \geq 1 - 2\dx.
	\end{align*}
\end{lemma}
\begin{proof}
	We take the binomial expansion of $(1 + x)^d$:
	\begin{align*}
	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
	\end{align*}

	The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
\end{proof}

@@

	% AJG 5/14/19: This argument makes sense, correct?
	We first consider the term $\Sigma_k$. $\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$. Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero). As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
	\begin{equation}
	\label{eqn: slice_volume_bound}
	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
	\end{equation}
	which in turn gives
	\begin{align}
	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (u_{i,k} = t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
	\end{align}
	\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
	\begin{align}
	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
	& \overset{(i)}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
	\end{align}
	where $(i)$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.

	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
	\begin{align}
	\xi & \overset{(ii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
	& \overset{(iii)}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}. \label{eqn: xi_ub}
	\end{align}
	where $(ii)$ follows from \eqref{eqn: slice_volume_bound}, and $(iii)$ from Lemma \ref{lem: Taylor_series}. As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
\end{proof}

@@

\begin{lemma}
	\label{lem: beta_integral}
	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write 
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
	\end{equation*}
	The first integral is simply the beta function, with
	\begin{equation*}
	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
	\end{equation*}
	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
	\begin{equation*}
	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
	\end{equation*}
	As a result,
	\begin{align*}
	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
	& \overset{(iv)}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
	& =  3\alpha^{1/2}.
	\end{align*}
	where $(iv)$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
\end{proof}

@@

\begin{lemma}
	\label{lem: tv_to_uniform_distance}
	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
	\begin{equation*}
	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
	\end{equation*}
\end{lemma}
\begin{proof}
	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
	\begin{align}
	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
	& \overset{(i)}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
	\end{align}
	where $(i)$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.

@@

	From here, some simple manipulations yield
	\begin{align}
	\nu(\Csig \cap I)  & = \nu(I) - \nu(I \setminus \Csig) \nonumber \\
	& \geq \nu(I) - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
	\end{align}
	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
\end{proof}

>>>>

\newcommand{\sbcomment}[1]{{\color{red} \bf{{{{SB --- #1}}}}}}

@@

Subsections \ref{sec: volume_estimates} - \ref{sec: proof_of_theorem_1} detail the proof for Theorem \ref{thm: conductance_upper_bound}. In subsections \ref{sec: mixing_time_on_graphs} and \ref{sec: proof_of_proposition_tv_mixing_time}, we establish some results regarding mixing time over general graphs. The proof of Theorem \ref{thm: mixing_time_upper_bound} is then provided in subsections \ref{sec: population_conductance_function} - \ref{sec: proof_of_theorem_mixing_time}. Section~\ref{sec: concentration} gives some general concentration results we use throughout, before we finish with the proofs of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, and the statement and proof of our results regarding the a\pprspace vector (Corollary \ref{cor: appr}), in subsections \ref{sec: proof_of_misclassification_rate} - \ref{sec: linalg}.

@@

Lemma \ref{lem: expansion_volume} provides a bound on the ratio $\nu(\Csig + r B) / \nu(\Csig)$, an important intermediate quantity in bounding the ratio $\cut(\Csig[\Xbf]; G_{n,r})/\vol(\Csig[\Xbf]; G_{n,r})$.

@@

	We next show a lower bound on $\nu(\Asig)$. Partition $\Asig$ using the balls $B(x_i,\sigma)$, meaning let $\Aset_{\sigma}^{(1)} := B(x_1,\sigma)$, $\Aset_{\sigma}^{(2)} := B(x_2,\sigma) \setminus B(x_1,\sigma)$, and so on, so that
	\begin{equation*}
	\Aset_{\sigma}^{\text{(i)}} := B(x_i,\sigma) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma}^{(j)}. \tag{$i = 1,\ldots,N$}
	\end{equation*}
	Observe that $\bigcup_{i = 1}^{N} \Asig^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma)$, so by \eqref{eqn: finite_subcover} $\Asig \supseteq \bigcup_{i = 1}^{N} \Asig^{\text{(i)}}$. As $\Asig^{(1)},\ldots, \Asig^{(N)}$ are non-overlapping,
	\begin{align*}
	\nu(\Asig) & \geq \sum_{i = 1}^{N} \nu(\Asig^{\text{(i)}}) \\
	& = \sigma^d \nu_d \sum_{i = 1}^{N}  \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
	\end{align*}
	We turn to proving an analogous upper bound on $\nu(\Asig + \delta B)$. Let $\Aset_{\sigma + \epsilon + \delta}^{(1)} := B(x_1,\sigma + \delta + \epsilon)$ and
	\begin{equation*}
	\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} := B(x_i,\sigma + \delta + \epsilon) \setminus \bigcup_{j = 1}^{i - 1} \Aset_{\sigma + \delta + \epsilon}^{(j)}. \tag{$i = 2,\ldots,N$}
	\end{equation*}
As $\bigcup_{i = 1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}} = \bigcup_{i = 1}^{N} B(x_i,\sigma + \delta + \epsilon)$, by \eqref{eqn: finite_subcover}
	\begin{equation*}
	\Aset_{\sigma} + \delta B \subset \bigcup_{i =1}^{N} \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}
	\end{equation*}
	and therefore \sbcomment{Added a subscript $\sigma$ on LHS}
	\begin{align*}
	\nu(\Aset_\sigma + \delta B) & \leq \sum_{i = 1}^{N} \nu\bigl(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}\bigr) \\
	& = \sum_{i = 1}^{N} \nu_d (\sigma + \delta + \epsilon)^d \frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \\
	& \leq \nu_d (\sigma + \delta + \epsilon)^d \sum_{i = 1}^{N} \frac{\nu(\Asig^{\text{(i)}})}{\nu(B(x_i,\sigma))}
	\end{align*}
	where the last inequality follows from Lemma \ref{lem: covering}. We have shown \eqref{eqn: ratio_of_volume}, and thus the claim.
\end{proof}
\noindent We require Lemma \ref{lem: covering} to prove Lemma \ref{lem: expansion_volume}.
\begin{lemma}
	\label{lem: covering}\sbcomment{Changed $A$ to $\Aset$ in the statement}
	For $i = 1, \ldots, N$ and  $\Aset_{\sigma}^{\text{(i)}}, \Aset_{\sigma + \delta + \epsilon}^{\text{(i)}}$ as in Lemma \ref{lem: expansion_volume},
	\begin{equation*}
	\frac{\nu(\Aset_{\sigma + \delta + \epsilon}^{\text{(i)}})}{\nu(B(x_i, \sigma + \delta + \epsilon))} \leq \frac{\nu(\Aset_{\sigma}^{\text{(i)}})}{\nu(B(x_i, \sigma))}
	\end{equation*}
\end{lemma}
\begin{proof}
	Let $\delta' := \delta + \epsilon$. It will be sufficient to show that
	\begin{equation*}
	\biggl(\Aset_{\sigma + \delta'}^{\text{(i)}} - \set{x_i}\biggr) \subseteq \left(1 + \frac{\delta'}{\sigma}\right)\cdot\biggl(\Asig^{\text{(i)}} - \set{x_i}\biggr) 
	\end{equation*}
	since then
	\begin{equation*}
	\nu(\Aset_{\sigma + \delta'}^{\text{(i)}}) \leq \left(1 + \frac{\delta'}{\sigma}\right)^d \nu(\Aset_{\sigma}^{\text{(i)}}) = \frac{\nu(B(x_i, \sigma + \delta'))}{\nu(B(x_i, \sigma))} \nu(\Aset_{\sigma}^{\text{(i)}}).
	\end{equation*}

	Assume without loss of generality that $x_i = 0$, and let $x \in \Aset_{\sigma + \delta'}^{\text{(i)}}$, meaning
	\begin{equation}
	\norm{x} \leq \sigma + \delta',~ \norm{x - x_j} > \sigma + \delta'~ \textrm{for $j = 1, \ldots, i - 1$}.
	\end{equation}
	Letting $x' = \frac{\sigma}{\sigma + \delta'} x$, since $\norm{x} \leq \sigma + \delta'$, $\norm{x'} \leq \sigma$ and therefore $x' \in B(0,\sigma)$. Additionally observe that for any $j = 1, \ldots, i - 1$, by the triangle inequality
	\begin{equation*}
	\norm{x' - x_j} \geq \norm{x - x_j} - \norm{x - x'} > \sigma + \delta' - \frac{\delta'}{\sigma + \delta'}\norm{x} \geq \sigma
	\end{equation*}
	and therefore $x' \not\in B(x_j,\sigma)$ for any $j = 1,\ldots, i - 1$. So $x' \in \Asig^{\text{(i)}}$.
\end{proof}

We will need to carefully control the volume of expansion sets using the estimate in Lemma~\ref{lem: expansion_volume}; Lemma~\ref{lem: Taylor_series} serves this purpose (see also, Lemma~23 in \cite{balakrishnan2013}). 
\begin{lemma}
	\label{lem: Taylor_series}
	For any $0 \leq x \leq 1/2d$,
	\begin{align*}
	(1 + x)^d & \leq 1 + 2\dx \\
	(1 - x)^d & \geq 1 - 2\dx.
	\end{align*}
\end{lemma}
\begin{proof}
	We take the binomial expansion of $(1 + x)^d$:
	\begin{align*}
	(1 + x)^d & = \sum_{k = 0}^{d} {d \choose k} x^k \\
	& = 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k} x^{k - 1}}{d}\right)\\
	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{{d \choose k}}{(2d)^{k-1}d}\right) \tag{since $x \leq \frac{1}{2d}$} \\
	& \leq 1 + \dx + \dx\left(\sum_{k = 2}^d \frac{1}{2^{k - 1}}\right) \leq 1 + 2\dx.
	\end{align*}
The proof for the corresponding lower bound on $(1 - x)^d$ is symmetric.
\end{proof}

@@

	% AJG 5/14/19: This argument makes sense, correct?
	We first consider the term $\Sigma_k$. $\Cset$ has finite diameter by \ref{asmp: bounded_density}, as otherwise $\int_{\Csig} f(x) dx = \infty$. Letting $\overline{\Cset}$ be the closure of $\Cset$, we observe that $\overline{\Csig} = \overline{\Cset} + \sigma B$, and moreover for any $\delta > 0$, $\nu(\overline{\Csig} + \delta B) = \nu(\Csig + \delta B)$ (as the boundary $\partial(\Csig + \delta B)$ is Lipschitz and therefore has measure zero). As a result, for each $t_{i,k}, i = 1, \ldots,k$ we may apply Lemma \ref{lem: expansion_volume} to $\overline{\Cset}$ and obtain
	\begin{equation}
	\label{eqn: slice_volume_bound}
	\nu_{i,k} = \nu(\Csig + rt_{i,k}B) \leq \nu(\Csig)\left(1 + \frac{rt_{i,k}}{\sigma}\right)^d
	\end{equation}
	which in turn gives
	\begin{align}
	\Sigma_k & \leq c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ rt_{i,k}}{\sigma}\right)^d \biggl( (t_{i,k})^{\gamma} - (t_{i-1,k})^{\gamma}\biggr) \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}).~~~~~~~~~~~~~~ (u_{i,k} = t_{i,k}^{\gamma}) \label{eqn: Sigmak_riemann_sum}
	\end{align}
	The expression in~\eqref{eqn: Sigmak_riemann_sum} is a Riemann sum, and taking the limit as $k \to \infty$ we obtain
	\begin{align}
	\lim_{k \to \infty} c_0\nu(\Csig) r^\gamma \sum_{i = 1}^{k} \left(1 + \frac{ru_{i,k}^{1/\gamma}}{\sigma}\right)^d ( u_{i,k} - u_{i,k-1}) & = c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{r u^{1/\gamma}}{\sigma}\right)^{d} du \nonumber \\
	& \overset{\text{(i)}}{\leq} c_0\nu(\Csig) r^\gamma \int_{0}^{1} \left(1 + \frac{2 d r u^{1/\gamma}}{\sigma}\right) du \nonumber \\
	& = c_0\nu(\Csig) r^\gamma \left(1 + \gamma \frac{2 d r}{(\gamma + 1)\sigma}\right). \label{eqn: Sigmak_integral}
	\end{align}
	where $\text{(i)}$ follows from Lemma \ref{lem: Taylor_series} in light of the fact $r \leq \sigma / 2d$.

	An upper bound on $\xi$ follows from largely the same logic, although it does not involve integration:
	\begin{align}
	\xi & \overset{\text{(ii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{ r}{\sigma}\right)^d(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} \nonumber \\
	& \overset{\text{(iii)}}{\leq} \nu(\Csig) \biggl\{ \left(1 + \frac{2d r}{\sigma}\right)(\lambda_{\sigma} - c_0r^{\gamma}) - \lambda_{\sigma} \biggr\} = \nu(\Csig) \biggl\{ \frac{2dr}{\sigma}(\lambda_{\sigma} - c_0r^{\gamma}) - c_0 r^{\gamma} \biggr\}. \label{eqn: xi_ub}
	\end{align}
	where $\text{(ii)}$ follows from \eqref{eqn: slice_volume_bound}, and $\text{(iii)}$ from Lemma \ref{lem: Taylor_series}. As the bounds in \eqref{eqn: partition_ub} and \eqref{eqn: telescoping_sum} hold for all $k$, these along with \eqref{eqn: Sigmak_integral} and \eqref{eqn: xi_ub} imply the desired result.
\end{proof}

@@

\begin{lemma}
	\label{lem: beta_integral}
	For any $0 \leq t \leq 1$ and $\alpha \leq \frac{t^2}{16 d}$,
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du \geq \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)} - \frac{3t}{4\sqrt{d}}
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write 
	\begin{equation*}
	\int_{0}^{1 - \alpha}u^{(d-1)/2}(1 - u)^{-1/2}du = \int_{0}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du - \int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du
	\end{equation*}
	The first integral is simply the beta function, with
	\begin{equation*}
	B(\frac{d+1}{2},\frac{1}{2}) := \frac{\Gamma\bigl(\frac{d + 1}{2}\bigr)\Gamma\bigl(\frac{1}{2}\bigr)}{ \Gamma\bigl(\frac{d}{2}+ 1\bigr)}.
	\end{equation*}
	To upper bound the second integral, we expand $(1 - u)^{-1/2}$ around $u = 1 - \alpha$, obtaining
	\begin{equation*}
	(1 - u)^{-1/2} \leq \alpha^{-1/2} + \max_{u \in (1 - \alpha, 1)} \frac{\alpha}{2} (1 - u)^{-3/2} = \frac{3}{2}\alpha^{-1/2}.
	\end{equation*}
	As a result,
	\begin{align*}
	\int_{1 - \alpha}^{1}u^{(d-1)/2}(1 - u)^{-1/2}du & \leq \frac{3}{2}\alpha^{-1/2} \int_{1 - \alpha}^{1}u^{(d-1)/2}du \\
	& = \frac{3}{d+1}\alpha^{-1/2} \left(1 - (1 - \alpha)^{(d + 1)/2}\right) \\
	& \overset{\text{(iv)}}{\leq} \frac{3}{(d+1)}\alpha^{-1/2} (\alpha(d + 1)) \\
	& =  3\alpha^{1/2}.
	\end{align*}
	where $\text{(iv)}$ follows from Lemma \ref{lem: Taylor_series}, and the fact $\alpha \leq \frac{1}{16d}$. The result follows from the condition $\alpha \leq \frac{t^2}{16d}$. 
\end{proof}

@@

\begin{lemma}
	\label{lem: tv_to_uniform_distance}
	Let $\norm{q_v^{(t)} - \pi}_{TV} \leq \frac{1}{14} \max \set{1, \frac{1}{s(G)}}$. Then,
	\begin{equation*}
	d_{\mathrm{unif}}(q_v^{(t + 3)},\pi) \leq \frac{1}{4}
	\end{equation*}
\end{lemma}
\begin{proof}
	Fix $u \in V$ and let $m \geq t + 1$ be arbitrary. The stationarity of $\pi$ gives
	\begin{align}
	\frac{\pi(u) - q_v^{m}(u)}{\pi(u)} & = \sum_{y \in V} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) \nonumber \\
	& \overset{\text{(i)}}{=} \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{\pi(u)} \left(\frac{1}{2} - \pi(u)\right) \nonumber \\
	& \leq \sum_{y \neq u} \left(\pi(y) - q^{(m-1)}(v,y)\right) \left(\frac{q^{(1)}(y,u) - \pi(u)}{\pi(u)}\right) + \frac{\pi(u) - q^{(m - 1)}(v,u)}{2 \pi(u)} \label{eqn: tv_to_uniform_distance_1}
	\end{align}
	where $\text{(i)}$ follows from $q^{(1)}(u,u) = \frac{1}{2}$.

@@

	From here, some simple manipulations yield
	\begin{align}
	\nu(\Csig \cap I)  & = \nu\text{(i)} - \nu(I \setminus \Csig) \nonumber \\
	& \geq \nu\text{(i)} - \max \set{\nu\bigl(B(u,r) \setminus \Csig\bigr), \nu\bigl(B(v,r) \setminus \Csig\bigr)} \nonumber \\
	& \geq \nu_d r^d \left(1 - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}} - (1 -\ell) \label{eqn: one_step_2} \right) = \nu_d r^d\left(\ell - \frac{3 \sqrt{3} t}{4\sqrt{2\pi}}\right)
	\end{align}
	where the last inequality follows from Lemma \ref{lem: overlap_balls_1}. \eqref{eqn: one_step_2} along with \eqref{eqn: one_step_1} then give the desired result.
\end{proof}
